Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2012-05-22 ms.tex
bayestar-localization: TeXified some equations that are in my lab notebook
bayestar-localization: fixed error in Fisher matrix

	\frac{\partial^2 \log \mathcal{L}}{\partial A \partial B} &=
	\frac{\partial^2 \log \mathcal{L}}{\partial A \partial t_0} =
	\frac{\partial^2 \log \mathcal{L}}{\partial B \partial t_0} = 0 \\

@@

The first two terms of $\mathcal{I}_{t_0,t_0}$ vanish because the integrands $|\tilde{a}(f)|^2 f / S(f)$ and $|\tilde{b}(f)|^2 f / S(f)$ are odd about $f = 0$.  We assume that $\tilde{a}(f)$ and $\tilde{b}(f)$ are orthogonal with respect to $\emph{any}$ real weight, including both $S(f)$ and $S(f) / f^2$, so the last term in $\mathcal{I}_{t_0,t_0}$ vanishes as well.  Further,%

@@

>>>>

	\frac{\partial^2 \log \mathcal{L}}{\partial A \partial B} &= 0 \\
	\frac{\partial^2 \log \mathcal{L}}{\partial A \partial t_0} &=
	2 \pi i \int \frac{\left(\tilde{a}^*(f) \tilde{x}(f) e^{2 \pi i f t_0} - \tilde{a}(f) \tilde{x}^*(f) e^{-2 \pi i f t_0}\right)}{S(f)} f \mathrm{d}f \\
	\frac{\partial^2 \log \mathcal{L}}{\partial B \partial t_0} &=
	2 \pi i \int \frac{\left(\tilde{b}^*(f) \tilde{x}(f) e^{2 \pi i f t_0} - \tilde{b}(f) \tilde{x}^*(f) e^{-2 \pi i f t_0}\right)}{S(f)} f \mathrm{d}f \\

@@

$\mathcal{I}_{A,t_0}$, $\mathcal{I}_{B,t_0}$, and the first two terms of $\mathcal{I}_{t_0,t_0}$ vanish because the integrands $|\tilde{a}(f)|^2 f / S(f)$ and $|\tilde{b}(f)|^2 f / S(f)$ are odd about $f = 0$.  We assume that $\tilde{a}(f)$ and $\tilde{b}(f)$ are orthogonal with respect to $\emph{any}$ real weight, including both $S(f)$ and $S(f) / f^2$, so the last term in $\mathcal{I}_{t_0,t_0}$ vanishes as well.  Further,%

@@

\section{Equations that need to be organized}

\begin{equation}
	u = \cos \iota
\end{equation}

\begin{equation}
	\mathbf{G} =
	\left(
		\begin{array}{cccc}
			F_+^1 D_1^1 & F_+^2 D_1^2 & \cdots & F_+^N D_1^N \\
			F_\times^1 D_1^1 & F_\times^2 D_1^2 & \cdots & F_\times^N D_1^N
		\end{array}
	\right)
\end{equation}

\begin{equation}
	\mathbf{H} = \mathbf{G}\mathbf{G}^\mathsf{T} =
	\left(
		\begin{array}{cc}
			\sum \left(F_+^i D_1^i\right)^2 & \sum \left(F_+^i D_1^i\right)\left(F_\times^i D_1^i\right) \\
			\sum \left(F_+^i D_1^i\right)\left(F_\times^i D_1^i\right) & \sum \left(F_\times^i D_1^i\right)^2
		\end{array}
	\right)
\end{equation}

\begin{equation}
	\mathbf{R} =
	\left(
		\begin{array}{cc}
			\cos \phi & \sin \phi \\
			-\sin \phi & \cos \phi
		\end{array}
	\right)
	\left(
		\begin{array}{cc}
			\frac{1}{2} (1 + u^2) & 0 \\
			0 & u
		\end{array}
	\right)
	\left(
		\begin{array}{cc}
			\cos \psi & \sin \psi \\
			-\sin \psi & \cos \psi
		\end{array}
	\right) \mathbf{G}
\end{equation}

\begin{equation}
	p = \Tr \mathbf{R}^\mathsf{T} \mathbf{R}
	= \frac{1}{8} \left\{
		\left(u^4 + 6 u^2 + 1\right) \left(H_{11} + H_{22}\right) + (1 - u^2)^2
		\left[ \left( H_{11} - H_{22} \right) \cos 2\psi + 2 H_{12} \sin 2\psi \right]
	\right\}
\end{equation}

\begin{equation}\fl
	q = \sqrt{(ab - cd) (u + u^3) + \frac{1}{8} \left\{ (a^2 + b^2 + c^2 + d^2)(u^4 + 6u^2 + 1) + (1 - u^2)^2 \left[ (a^2 - b^2 - c^2 + d^2) \cos 2\psi + 2(ac + bd) \sin 2\psi \right] \right\}}
\end{equation}
